\documentclass{cce2014-meetings}
\svnInfo $Id: minutes_week09.tex 7640 2024-03-13 16:42:14Z jbri2 $

% Meeting details
\title{Meeting Minutes -- Group 4}
\author{Location: 0 B 6}
\date{30 April 2024, 15:00--20:00}

\begin{document}

\maketitle

\section*{Present}
% Members present at the meeting
Alessandro Parrella,
Gabriel Vella,
Jonas Rousseau-Morvan,
Keith Farrugia

\section*{Discussion}

\begin{enumerate}

      % There should be an item corresponding to each of the agenda items for
      % this meeting.

      \item Minutes from the previous meeting were read and approved.

      \item No matters arose from previous meetingsa

      \item Progress report from group members
            \begin{enumerate}
                  \item Jonas and Keith reported that the DTMF decoding is working.
                  There is a slight chance of incorrect readings, but these do not 
                  affect heavily the results due to the invalid readings buffer. 
                  One possible solution is to amplify the line level input. This 
                  was shown to increase goertzel accuracy.
                  \item Keith soldered the line-level input circuit to a 
                  prototyping board that needs testing. The risk of damaging 
                  compoenets during transportation is decreased.
                  \item Gabriel and Allessandro worked on buttons
            \end{enumerate}

      \item Targets set for the week
            \begin{enumerate}
                  \item Work on buttons 
                  \item Start report.  
            \end{enumerate}
            
      \item No other matters were discussed
\end{enumerate}

\section*{Actions}

\begin{enumerate}

      \item Work on auto-scroll
      \begin{flushright}
            Assigned to: \textbf{Jonas Rousseau Morvan}\\
            Deadline: \textbf{next meeting}
      \end{flushright}

      \item Work on reformatting and Optimisation
      \begin{flushright}
            Assigned to: \textbf{Keith Farrugia}\\
            Deadline: \textbf{next meeting}
      \end{flushright}

      \item Continue implementing buttons
      \begin{flushright}
            Assigned to: \textbf{Gabriel Vella and Alessandro Parella}\\
            Deadline: \textbf{next meeting}
      \end{flushright}
      % Add more actions as necessary

\end{enumerate}

\end{document}
