\documentclass{cce2014-meetings}
\svnInfo $Id: minutes_week02.tex 7640 2024-02-21 08:19:14Z jbri2 $

% Meeting details
\title{Meeting Minutes -- Group 4}
\author{Location: Common Room and It services Common Room}
\date{21 February 2024, 17:00--20:00}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Alessandro Parrella,
Gabriel Vella (Chair),
Keith Farrugia,
Jonas Rousseau-Morvan


\section*{Discussion}

\begin{enumerate}

   % There should be an item corresponding to each of the agenda items for this
   % meeting.
   \item Progress report from group members:
         \begin{enumerate}
            \item Gabriel Vella reported that he was able to get the circuit
            \item Keith Farrugia and Jonas Rousseau-Morvan reported that they have downloaded the MDK‐ARM Microcontroller Development Kit
            \item All members reported that they have downloaded SVN (Jonas still needs access).
            \item All members completed the "Getting Started" lab.
            \item All members formed the general basic concept for the project.
         \end{enumerate}

   \item Targets set for the week:
         \begin{enumerate}
            \item Retrieve the circuit board and cables.
            \item Read through the handbook.
            \item Install the necessary programs, and drivers and download the material such as labs.
            \item We should take a look at the "Getting Started", and test out the first lab to check if everything was set up right.
            \item Form a general basic concept for the project.
            \item Assign research material for this week.
         \end{enumerate}
         
   \item Other matters
         \begin{enumerate}
            \item First item discussed that was not on the agenda was the availabilities of the group members
         \end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

   \item Research how to control/set up ADC.
         \begin{flushright}
            Assigned to: \textbf{Keith Farrugia} \\
            Deadline: \textbf{next meeting}
         \end{flushright}

   \item Research on how to compute the frequency to bit size equation.
         \begin{flushright}
            Assigned to: \textbf{Jonas Rousseau-Morvan} \\
            Deadline: \textbf{next meeting}
         \end{flushright}

   \item Research about Fourier Transform in C.
         \begin{flushright}
            Assigned to: \textbf{Alessandro Parrella} \\
            Deadline: \textbf{next meeting}
         \end{flushright}

   \item Research about digital input (button press) and output (LED for status indications).
         \begin{flushright}
            Assigned to: \textbf{Gabriel Vella} \\
            Deadline: \textbf{next meeting}
         \end{flushright}

   \item Research about LCD Screen.
         \begin{flushright}
            Assigned to: \textbf{Gabriel Vella} \\
            Deadline: \textbf{next meeting}
         \end{flushright}

\end{enumerate}

\end{document}
